\documentclass[10pt]{article}
\title{}
\usepackage[margin=1.27cm]{geometry}
\usepackage{array}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[export]{adjustbox}
\usepackage{setspace}
\usepackage{mdframed}
\setlength{\parindent}{0pt}
\usepackage{hyperref}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={purple!50!black},
    citecolor={purple!50!black},
    urlcolor={purple!80!black}
}
\pagenumbering{gobble}
\date{}
\begin{document}

	{\centering{\huge{\textsc{Chandramowli J}}}}
	\hfill {\fontfamily{cmtt}\selectfont{\href{mailto:jchandramowli@gmail.com}{jchandramowli@gmail.com}}} \hfill{	\fontfamily{cmtt}\selectfont{+91-9445640398}}
	\hfill{\href{https://github.com/chamow97}{GitHub}}
\hfill{\href{https://drive.google.com/open?id=0BznmPUIFiWMoNVlUVDRxTjVFMnM}{Certificates}}
	\vspace{1mm}
	\hrule
	\vspace{0.6mm}
	\hrule

	\vspace{4mm}
	
	{\Large{\textsc{Education}} \hrulefill}

	\vspace{2mm}
		
	\begin{tabular}{p{2.5cm} p{6.7cm} p{8.7cm} p{3cm}}	
	
	\textsc{April} 2019 & B.Tech \textsc{(Information Technology)} & \textsc{\href{http://www.ssn.edu.in/?page_id=124}{S.S.N College}} \hfill | \normalsize \fontfamily{cmtt}\selectfont{8.3/10}\\		
	\textsc{April} 2015 & Class XII \textsc {(CBSE)} & \normalsize\textsc{\href{http://davchennai.org/}{D.A.V Boys} -} Chennai \hfill{| \normalsize \fontfamily{cmtt}\selectfont{95.60\% }}\\
	\textsc{April} 2013 & Class X \textsc {(CBSE)} & \normalsize\textsc{\href{http://www.hinduseniortriplicane.com/}{The Hindu Senior Secondary} -} Chennai \hfill{| \normalsize \fontfamily{cmtt}\selectfont{ 10/10}}\\
	
	\end{tabular}
	\vspace{2mm}

	{\centering\Large{\textsc{Achievements}} \hrulefill}
		
	\begin{itemize}
	\setlength\itemsep{-0.25em}
	\item Placed \textsc{$3^{rd}$ in India}(top 0.3\%) and \textsc{$102^{nd}$ in World}(top 3\%) in \textsc{IEEExtreme 11.0}.
	\item \textsc{Runner Up}(top 2\%) in the \textsc{ACM ICPC Provincial Contest 2017} conducted by KCG College of Technology.
	\item Placed \textsc{$8^{th}$} in the \textsc{Shaastra Programming Contest - 2017} conducted by \textsc{IIT Madras}.
	\item \textsc{Winner}(top 1\%) of the Programming Contest conducted by \textsc{Anna University, Chennai}.
	\item Qualified(top 15\%) for the \textsc{CodeChef SnackDown Elimination Round 2017}.
	\item Secured an appreciation letter from \textsc{HRD Minister} for my performance in \textsc{AISSCE - 2015}(top 1\%).
	\item \textsc{Runner Up} in the \textsc{IEEE Student Branch Website Development} Competition in the Madras Section.
	\item Active participant with handle \textbf{chamow} in Online Programming Competitions and have solved over 500 problems.

	
	\end{itemize}
	\vspace{2mm}
	{\centering\Large{\textsc{Internship}}	\hrulefill}
	
	\vspace{2mm}
	
	\large\textsc{\href{http://planezy.com/}{PLANezy}}
	\hfill{\small{\textsc{Jun '17 - Aug '17}}}
	
	\begin{changemargin}{1.0cm}{0.0cm} 
	{
	\large{\textsc{{Backend Development}}}  \\
	\small{Worked with \textsc{Laravel Framework}(PHP) and with \textsc{MySQL} to redesign User and Vendor Dashboard. Implemented Like and Bookmark functionality for the images. Created ER Diagram for their Database and revamped their website by adding new relations and removing unncessary ones.} 		
	}
	\end{changemargin} 	 	
	\vspace{2mm}

	{\centering\Large{\textsc{Projects}} \hrulefill}
		
	\vspace{3mm}
	
	\large{\textsc{\href{https://github.com/chamow97/Algorithm-DS-Library}{Algorithms and Data Structures Library}}   \hfill \small\textsc{Nov '16 - Present}
	\begin{itemize}
	\small
	{
	\item Implementation of basic and advanced Algorithms and Data Structures in C++ such as Segment Trees, Shortest Path Algorithms, Trie, Knapsack variants etc.
	}
	\end{itemize}	
	\vspace{2mm}
	\large{\textsc{\href{https://github.com/chamow97/SSNCB}{SSN Code Busters}}}   \hfill \small\textsc{June '17 - Present}
	\begin{itemize}
	\small
	{
	\item An online Programming Judge like HackerEarth for my college developed using Django(Python) which is funded by my college.
	}
	\end{itemize}	
	\vspace{2mm}
	\large{\textsc{\href{https://github.com/chamow97/snappy}{Snappy}}}   \hfill \small\textsc{Feb '17 - April '17}
	\begin{itemize}
	\small
	{
	\item A web app which gets all the images tagged with the given tag from Twitter and Tumblr and displays it as a Gallery filtering out NSFW images.
	}
	\end{itemize}	
	\vspace{3mm}
	
		{\centering\Large{\textsc{Technical Skills}}\hrulefill}
	
	\vspace{3mm}

	\normalsize{
	\textsc{Programming Languages:} \textsc{C, C++, Python(basic), JavaScript(basic).} \\
	\textsc{Tools/Frameworks:} \textsc{Bootstrap, Django, Git, SQL, Laravel(basic).}
	}\\
	\textsc{Interests:} \textsc{Algorithms, Data Structures, Competitive Programming.}
			
	\vspace{4mm}
		{\centering\Large{\textsc{Relevant Courses}}\hrulefill}
		
	\vspace{4mm}
	\large{\textsc{University Courses}}
	\vspace{2mm}
	\begin{small}
	
	\begin{tabular}{p{7.2cm} p{5.7cm} p{6cm}}
	{Computer Architecture} & {Database Management System} &{Design and Analysis of Algorithms}\\
	{Operating System} & {Programming and Data Structures} &	{Software Engineering}\\
	\end{tabular}
	
	\end{small}
	\vspace{2mm}
	\large{\textsc{Online Courses}}
	\vspace{2mm}
	\begin{small}
	
	\begin{tabular}{p{9.2cm} p{6.7cm} p{6cm}}
	{Coursera: Algorithm Design and Analysis(Stanford University)} & {NPTEL: Algorithms(IIT Kanpur)}
	\vspace{3mm}
	\end{tabular}
	
	\end{small}
	\vspace{3mm}
	{\centering\Large{\textsc{Positions of Responsibility}}	\hrulefill}
		
	\vspace{3mm}		
	\setlength\itemsep{-0.25em}
	\begin{normalsize}
	
	\begin{itemize}

	\item One of the Competitive Coding Mentors of Coding Club of my Department. Have conducted 10 classes on Math Theory, Shortest Path, Dynamic Programming, Segment Trees etc.
	\item \textsc{Web Architect} of \textsc{\href{https://github.com/SSN-IEEE}{IEEE Student Branch}} of my College.
	\end{itemize}	
	\end{normalsize}
\end{document}

